Weak interspecific interactions in a sagebrush steppe: evidence from observations, models, and experiments

### 2017-01-13 removals/manuscript/removal_ms.tex
Moved data into ExperimentTest repository, changed paths in scripts accordingly

Funding was provided by NSF grants DEB-1353078,and  DEB-1054040 to PBA and DEB 1353039 to SPE, and by the Utah Agricultural Experiment Station (get journal paper number). The USDA-ARS Sheep Experiment Station generously provided access to historical data and the field experiment site.  We thank Robin Snyder for suggestions that improved the manuscript.

>>>>

Funding was provided by NSF grants DEB-1353078,and  DEB-1054040 to PBA and DEB-1353039 to SPE, and by the Utah Agricultural Experiment Station (get journal paper number). The USDA-ARS Sheep Experiment Station generously provided access to historical data and the field experiment site.  We thank Robin Snyder for suggestions that improved the manuscript.
